### 2024-04-01 doc/sections/mav-mechanisation.tex
Use interact/co-interact

As well as giving confidence in our results, a key benefit of
formalising the development in a proof assistant like Agda is that the
proof normalisation process (\Cref{thm:cut-elim}) is executable. For
example, we can normalise the one step MAV proof using
\cref{rule:Axiom} of $\vP \vParr \vDual{\vP}$ where
$\vP = (\vUnit \vPlus \vUnit) \vSeq (\vUnit \vWith \vUnit)$ to a 38
step (of which 9 are $\vInferFrom$ steps) normal proof, presented
online in Agda notation here:
\begin{center}
  \url{https://bobatkey.github.io/semantic-cut-elimination/MAV.Example.html#908}
\end{center}

>>>>

As well as giving confidence in our results, a key benefit of
formalising the development in a proof assistant like Agda is that the
proof normalisation process (\Cref{thm:cut-elim}) is executable. For
example, we can normalise the one step MAV proof using
\cref{rule:Interact} of $\vP \vParr \vDual{\vP}$ where
$\vP = (\vUnit \vPlus \vUnit) \vSeq (\vUnit \vWith \vUnit)$ to a 38
step (of which 9 are $\vInferFrom$ steps) normal proof, presented
online in Agda notation here:
\begin{center}
  \url{https://bobatkey.github.io/semantic-cut-elimination/MAV.Example.html#908}
\end{center}

### 2024-04-01 doc/sections/mav-syntax.tex
Use interact/co-interact

Beautifully, internalising branching makes the symmetry between the axiom and cut plain to see.

@@

\emph{Inference}, written $\vInferFrom$, is the smallest relation defined by the following axioms:
% NOTE: These shenanigans are for cross-text table alignment.
\newlength{\vInferFromDefnWidthOfLBL}%
\settowidth{\vInferFromDefnWidthOfLBL}{$\RuleName{AtomAxiom}$}%
\newlength{\vInferFromDefnWidthOfLHS}%
\settowidth{\vInferFromDefnWidthOfLHS}{$(\vP\vSeq\vQ)\vParr(\vR\vSeq\vS)$}%
\newlength{\vInferFromDefnWidthOfRHS}%
\settowidth{\vInferFromDefnWidthOfRHS}{$(\vP\vParr\vR)\vWith(\vQ\vParr\vR)$}%
\begin{displaymath}
  \begin{array}{lcl@{\hspace{0.5cm}}|@{\hspace{0.5cm}}l}
    \vP\vParr\vDual\vP
     & \vInferFrom
     & \vUnit
     & \makebox[\vInferFromDefnWidthOfLBL][l]{$\RuleLabel{Axiom}$}
    \\
    (\vP\vTens\vQ)\vParr\vR
     & \vInferFrom
     & \vP\vTens(\vQ\vParr\vR)
     & \RuleLabel{Switch}
    \\
    \vUnit\vWith\vUnit
     & \vInferFrom
     & \vUnit
     & \RuleLabel{Tidy}
    \\
    (\vP\vSeq\vQ)\vParr(\vR\vSeq\vS)
     & \vInferFrom
     & (\vP\vParr\vR)\vSeq(\vQ\vParr\vS)
     & \RuleLabel{Sequence}
    \\
    \vP\vPlus\vQ
     & \vInferFrom
     & \vP
     & \RuleLabel{Left}
    \\
    \vP\vPlus\vQ
     & \vInferFrom
     & \vQ
     & \RuleLabel{Right}
    \\
    (\vP\vWith\vQ)\vParr\vR
     & \vInferFrom
     & (\vP\vParr\vR)\vWith(\vQ\vParr\vR)
     & \RuleLabel{External}
    \\
    (\vP\vSeq\vQ)\vWith(\vR\vSeq\vS)
     & \vInferFrom
     & (\vP\vWith\vR)\vSeq(\vQ\vWith\vS)
     & \RuleLabel{Medial}
    \\
     &
     &
     &
    \\
    \vUnit
     & \vInferFrom
     & \vP\vTens\vDual\vP
     & \RuleLabel{Cut}
    \\
    \vUnit
     & \vInferFrom
     & \vUnit \vPlus \vUnit
     & \RuleLabel{CoTidy}
    \\
    (\vP\vTens\vR)\vSeq(\vQ\vTens\vS)
     & \vInferFrom
     & (\vP\vSeq\vQ)\vTens(\vR\vSeq\vS)
     & \RuleLabel{CoSequence}
    \\
    \vP
     & \vInferFrom
     & \vP\vWith\vQ
     & \RuleLabel{CoLeft}
    \\
    \vQ
     & \vInferFrom
     & \vP\vWith\vQ
     & \RuleLabel{CoRight}
    \\
    (\vP \vTens \vR) \vPlus (\vQ \vTens \vR)
     & \vInferFrom
     & (\vP \vPlus \vQ) \vTens \vR
     & \RuleLabel{CoExternal}
    \\
    (\vP \vPlus \vR) \vSeq (\vQ \vPlus \vS)
     & \vInferFrom
     & (\vP \vSeq \vQ) \vPlus (\vR \vSeq \vS)
     & \RuleLabel{CoMedial}
    \\
     &
     &
     &
    \\
    \vC\vPlug\vP\vInferFrom\vC\vPlug\vQ
     & \text{if}
     & \vP\vInferFrom\vQ
     & \RuleLabel{Mono}
    % \\
    % \vP\vInferFrom\vQ
    %  & \text{if}
    %  & \vP\vEquiv\vQ
    %  & \RuleLabel{Equiv}
  \end{array}
\end{displaymath}
If $\vP\vInferFrom\vQ$, we say that $\vP$ can be inferred from $\vQ$, \ie the arrow points from conclusion to premise.

The inference rules come in dual pairs. For every rule $\vP\vInferFrom\vQ$, there is a dual rule $\vDual\vP\vInferFrom\vDual\vQ$.
The exception is \cref{rule:Switch}, which is self-dual, up to commutativity.
The \cref{rule:Cut}, \cref{rule:CoLeft}, and \cref{rule:CoRight} rules introduce of new structures going left-to-right.
Normal proofs, which we define below, avoid these \emph{synthetic} rules.

@@

\begin{remark}
  In BV, the structural connectives are usually presented as lists, distinguished only by their brackets: $\vP\vTens\vQ$ is written as $\vls(\vP;\vQ)$; $\vP\vParr\vQ$ is written as $\vls[\vP;\vQ]$; and $\vP\vSeq\vQ$ is written as $\vls<\vP;\vQ>$.
  % The equations defining duality are usually included in the decidable equality on structures.
  Inferences, derivations, and proofs are presented vertically, as (\ref{notation:vlin}), (\ref{notation:vlde}), and (\ref{notation:vlpr}), respectively.
  \begin{center}
    $\inlineequation[notation:vlin]{%
        \vlderivation{\vlin{}{}{\vP}{\vlhy{\vQ}}}}$
    \qquad
    $\inlineequation[notation:vlde]{%
        \vlderivation{\vlde{}{}{\vP}{\vlhy{\vQ}}}}$
    \qquad
    $\inlineequation[notation:vlpr]{%
        \vlderivation{\vlpr{}{}{\vP}}}$
  \end{center}
  The relation between the deductive system for BV and rewrite systems is well-known, \eg by Kahramanogullari~\cite{Kahramanogullari08:maude}, who implements proof search for several deep inference systems in Maude~\cite{ClavelDELMMQ02:maude}.
  Inferences rules are usually named with the combination of a letter and an up or down arrow, \eg \cref{rule:Axiom} and \cref{rule:Cut} are $\iD$ and $\iU$, respectively.
\end{remark}

\begin{definition}\label{defn:normal}
  A derivation is \emph{normal} when it does not use \cref{rule:Cut} or any of the (\textsc{Co-X}) rules and its uses of \cref{rule:Axiom} are restricted to \cref{rule:AtomAxiom}, as defined by the following axiom:
  \begin{displaymath}
    \begin{array}{lcl@{\hspace{0.5cm}}|@{\hspace{0.5cm}}l}
      \makebox[\vInferFromDefnWidthOfLHS][l]{$\vNeg\va\vParr\vPos\va$}
       & \vInferFrom
       & \makebox[\vInferFromDefnWidthOfRHS][l]{$\vUnit$}
       & \RuleLabel{AtomAxiom}
    \end{array}
  \end{displaymath}
\end{definition}
Normal derivations avoid the use of rules that introduce new structures into proofs, and so can be termed \emph{analytic} in contrast to the need for the synthetic rules to synthesise new structures.

>>>>

Beautifully, internalising branching makes the symmetry between the axiom and cut plain to see. In BV, the axiom and cut rules are called \emph{interaction} and \emph{co-interaction}.

@@

\emph{Inference}, written $\vInferFrom$, is the smallest relation defined by the following axioms:
% NOTE: These shenanigans are for cross-text table alignment.
\newlength{\vInferFromDefnWidthOfLBL}%
\settowidth{\vInferFromDefnWidthOfLBL}{$\RuleName{AtomAxiom}$}%
\newlength{\vInferFromDefnWidthOfLHS}%
\settowidth{\vInferFromDefnWidthOfLHS}{$(\vP\vSeq\vQ)\vParr(\vR\vSeq\vS)$}%
\newlength{\vInferFromDefnWidthOfRHS}%
\settowidth{\vInferFromDefnWidthOfRHS}{$(\vP\vParr\vR)\vWith(\vQ\vParr\vR)$}%
\begin{displaymath}
  \begin{array}{lcl@{\hspace{0.5cm}}|@{\hspace{0.5cm}}l}
    \vP\vParr\vDual\vP
     & \vInferFrom
     & \vUnit
     & \makebox[\vInferFromDefnWidthOfLBL][l]{$\RuleLabel{Interact}$}
    \\
    (\vP\vTens\vQ)\vParr\vR
     & \vInferFrom
     & \vP\vTens(\vQ\vParr\vR)
     & \RuleLabel{Switch}
    \\
    \vUnit\vWith\vUnit
     & \vInferFrom
     & \vUnit
     & \RuleLabel{Tidy}
    \\
    (\vP\vSeq\vQ)\vParr(\vR\vSeq\vS)
     & \vInferFrom
     & (\vP\vParr\vR)\vSeq(\vQ\vParr\vS)
     & \RuleLabel{Sequence}
    \\
    \vP\vPlus\vQ
     & \vInferFrom
     & \vP
     & \RuleLabel{Left}
    \\
    \vP\vPlus\vQ
     & \vInferFrom
     & \vQ
     & \RuleLabel{Right}
    \\
    (\vP\vWith\vQ)\vParr\vR
     & \vInferFrom
     & (\vP\vParr\vR)\vWith(\vQ\vParr\vR)
     & \RuleLabel{External}
    \\
    (\vP\vSeq\vQ)\vWith(\vR\vSeq\vS)
     & \vInferFrom
     & (\vP\vWith\vR)\vSeq(\vQ\vWith\vS)
     & \RuleLabel{Medial}
    \\
     &
     &
     &
    \\
    \vUnit
     & \vInferFrom
     & \vP\vTens\vDual\vP
     & \RuleLabel{CoInteract}
    \\
    \vUnit
     & \vInferFrom
     & \vUnit \vPlus \vUnit
     & \RuleLabel{CoTidy}
    \\
    (\vP\vTens\vR)\vSeq(\vQ\vTens\vS)
     & \vInferFrom
     & (\vP\vSeq\vQ)\vTens(\vR\vSeq\vS)
     & \RuleLabel{CoSequence}
    \\
    \vP
     & \vInferFrom
     & \vP\vWith\vQ
     & \RuleLabel{CoLeft}
    \\
    \vQ
     & \vInferFrom
     & \vP\vWith\vQ
     & \RuleLabel{CoRight}
    \\
    (\vP \vTens \vR) \vPlus (\vQ \vTens \vR)
     & \vInferFrom
     & (\vP \vPlus \vQ) \vTens \vR
     & \RuleLabel{CoExternal}
    \\
    (\vP \vPlus \vR) \vSeq (\vQ \vPlus \vS)
     & \vInferFrom
     & (\vP \vSeq \vQ) \vPlus (\vR \vSeq \vS)
     & \RuleLabel{CoMedial}
    \\
     &
     &
     &
    \\
    \vC\vPlug\vP\vInferFrom\vC\vPlug\vQ
     & \text{if}
     & \vP\vInferFrom\vQ
     & \RuleLabel{Mono}
    % \\
    % \vP\vInferFrom\vQ
    %  & \text{if}
    %  & \vP\vEquiv\vQ
    %  & \RuleLabel{Equiv}
  \end{array}
\end{displaymath}
If $\vP\vInferFrom\vQ$, we say that $\vP$ can be inferred from $\vQ$, \ie the arrow points from conclusion to premise.

The inference rules come in dual pairs. For every rule $\vP\vInferFrom\vQ$, there is a dual rule $\vDual\vP\vInferFrom\vDual\vQ$.
The exception is \cref{rule:Switch}, which is self-dual, up to commutativity.
The \cref{rule:CoInteract}, \cref{rule:CoLeft}, and \cref{rule:CoRight} rules introduce of new structures going left-to-right.
Normal proofs, which we define below, avoid these \emph{synthetic} rules.

@@

\begin{remark}
  In BV, the structural connectives are usually presented as lists, distinguished only by their brackets: $\vP\vTens\vQ$ is written as $\vls(\vP;\vQ)$; $\vP\vParr\vQ$ is written as $\vls[\vP;\vQ]$; and $\vP\vSeq\vQ$ is written as $\vls<\vP;\vQ>$.
  % The equations defining duality are usually included in the decidable equality on structures.
  Inferences, derivations, and proofs are presented vertically, as (\ref{notation:vlin}), (\ref{notation:vlde}), and (\ref{notation:vlpr}), respectively.
  \begin{center}
    $\inlineequation[notation:vlin]{%
        \vlderivation{\vlin{}{}{\vP}{\vlhy{\vQ}}}}$
    \qquad
    $\inlineequation[notation:vlde]{%
        \vlderivation{\vlde{}{}{\vP}{\vlhy{\vQ}}}}$
    \qquad
    $\inlineequation[notation:vlpr]{%
        \vlderivation{\vlpr{}{}{\vP}}}$
  \end{center}
  The relation between the deductive system for BV and rewrite systems is well-known, \eg by Kahramanogullari~\cite{Kahramanogullari08:maude}, who implements proof search for several deep inference systems in Maude~\cite{ClavelDELMMQ02:maude}.
  Inferences rules are usually named with the combination of a letter and an up or down arrow, \eg \cref{rule:Interact} and \cref{rule:CoInteract} are $\iD$ and $\iU$, respectively.
\end{remark}

\begin{definition}\label{defn:normal}
  A derivation is \emph{normal} when it does not use \cref{rule:CoInteract} or any of the (\textsc{Co-X}) rules and its uses of \cref{rule:Interact} are restricted to \cref{rule:AtomInteract}, as defined by the following axiom:
  \begin{displaymath}
    \begin{array}{lcl@{\hspace{0.5cm}}|@{\hspace{0.5cm}}l}
      \makebox[\vInferFromDefnWidthOfLHS][l]{$\vNeg\va\vParr\vPos\va$}
       & \vInferFrom
       & \makebox[\vInferFromDefnWidthOfRHS][l]{$\vUnit$}
       & \RuleLabel{AtomInteract}
    \end{array}
  \end{displaymath}
\end{definition}
Normal derivations avoid the use of rules that introduce new structures into proofs, and so can be termed \emph{analytic} in contrast to the need for the synthetic rules to synthesise new structures.
